### 2013-07-30 mcmc.tex
something old
notes to self

@@

@@

...What plot should you make?  Make plots that demonstrate a non-converged and a converged chain.

...Autocorrelation time is the premier tool...
How is Autocorrelation time defined?..
How is Autocorrelation time measured?..
Why is it is not a panacea?..

@@

>>>>

...Why is it that the sampling is only really useful for computing integrals.  More on this below...

@@

...Reminder that a sampling is good for computing integrals (see above).
Therefore we should endeavor to use outputs that are based on integrals computed with the sampling.
This includes expectations and quantiles, but not optima...

@@

Making this heuristic condition more precise...
Autocorrelation time is the premier tool...
How is Autocorrelation time defined?..
How is Autocorrelation time measured?..
Why is it is not a panacea?..

...What plots should you make?
Make plots that demonstrate a non-converged and a converged chain...

@@

\paragraph{model checking:}
...Beyond the scope of this document...
Something about cross-validation and posterior predictive checks...
Something about plotting models (drawn from posterior) on data, where appropriate...
How could you possibly know that your sampling really represents your \emph{real} posterior PDF?..
